Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-07-17 GNproof.tex
revert back to proof lost in merge

Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$. If this set is empty, we are done. Otherwise, let $q \in Q_l \setminus Q_{l-1}$. By construction $q$ shares support with a propagator in $Q_{l-1}$. Call this propagator $p_j$. Let $v_j$ be the fourth vertex of $p_j$ in the $a_{j}-1$ ordering. Since $I_i(p_j) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$. We have two cases: $a_j-1 < v_j < j_m$ in any cyclic ordering, or $a_j-1 < j_m < v_j$. (Since $l \neq 0$, we cannot have $v_j = j_m$.) In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.  Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$. That is, $q \in \cP_{m-1}$, giving a contradiction.

Consider the second case ($a_j-1 < j_m < v_j$). {\color{violet}As above, $q$ shares support with $p_j$. More specifically, $a_j \in V(q)$.} By construction, $p_j$ must share support with some $p_r \in Q_{l-2}$. In particular, \hlfix{$a_j \pm 1  = a_r$, otherwise there would be crossing propagators}{The key here is that the contributing end of $p_j$ shares support with the contributing end of $p_r$. Which is on the inside is irrelevant. This is what forces $q$ to be inside both $p_r$ and $p_j$}. If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering. However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.

\begin{figure}[h]
\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$. Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
\end{figure} \sanote{This can't happen. $a_j \in V(q)$ by construction}

>>>>

\begin{figure}[h]
\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$. Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
\end{figure}
